---
title: "Nobel Prize Data Visualization"
author: "Chao Cui"
date: "2021/4/16"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load Data

```{r}
library(ggplot2)
library(dplyr)
library(scales)
library(stringr)
setwd('C:/Users/CUI/Downloads')
Prize <- read.csv("prize.csv")
Laureate <- read.csv("laureate.csv")
head(Prize) 
head(Laureate) 
```
## Clean Data
```{r }
mode(Laureate)
mode(Prize)
names(Laureate)
names(Prize)
sum(is.na(Laureate))
sum(is.na(Prize))
Laureate$bornCountry <- ifelse(str_detect(Laureate$bornCountry, "\\("), 
                               str_extract(Laureate$bornCountry, "(?<=\\().+?(?=\\))"),Laureate$bornCountry)
Laureate$diedCountry <- ifelse(str_detect(Laureate$diedCountry, "now"), 
                               str_extract(Laureate$diedCountry, "(?<=\\().*?(?=\\))"),Laureate$diedCountry)
Laureate$bornCountry <- ifelse(str_detect(Laureate$bornCountry, "now"), 
                               word(Laureate$bornCountry,-1),Laureate$bornCountry)
Laureate$diedCountry <- ifelse(str_detect(Laureate$diedCountry, "now"), 
                               word(Laureate$diedCountry,-1),Laureate$diedCountry)
Laureate$bornCountry <- str_replace_all(Laureate$bornCountry,"Scotland","United Kingdom")
Laureate$bornCountry <- str_replace_all(Laureate$bornCountry,"Northern Ireland","United Kingdom")
Laureate$diedCountry <- str_replace_all(Laureate$diedCountry,"Scotland","United Kingdom")
Laureate$diedCountry <- str_replace_all(Laureate$diedCountry,"Northern Ireland","United Kingdom")
```

## Q1: How many Nobel winner have been given in each category?
```{r }
tally(group_by(Prize,category))
arrange(tally(group_by(Prize,category)), n) %>% mutate(category=factor(category, levels=category)) %>%
ggplot(aes(x= category, y= n, fill = category))+ 
  geom_bar(stat = "identity", width = 0.8)+ geom_text(aes(label= n),nudge_y = 10) + 
  labs(title = "How many Nobel winners have been given in each category?", 
       x = "Category", y = "The number of Nobel winner")

```

## Q2: What is the gender ratio of Nobel Prize?

```{r }
tally(group_by(Laureate,gender)) %>% mutate(prop = round(n/sum(n),3)) %>%
  ggplot(aes(x="", y= prop,fill = gender)) + geom_bar(width = 1, stat = "identity")+ 
  geom_text(aes(label= percent(prop)),size=5,position = position_stack(vjust = 0.5))+ 
  labs(title = "The gender ratio of Noble Prize winners", x="", y = "")+
  coord_polar("y", start=1)+ theme(axis.ticks = element_blank(), 
                                                    axis.text.y = element_blank(),
                                                    axis.text.x = element_blank()) 
```

## Q3: What is the average age of Nobel Prize winners by category?
```{r }
Laureate %>% filter(substr(born,1,4) != "0000") %>% 
  mutate(prize_age = as.numeric(year) - as.numeric(substr(born,1,4))) %>% group_by(category)%>% 
  summarise( mean_prize_age = mean(prize_age)) %>% 
  ggplot(aes(x= category, y = mean_prize_age, fill= category)) + geom_bar(stat = "identity") +
  labs(x= "Category", y ="Average age of the prize winners",title = "Average age of Nobel Prize winners by category")+geom_text(aes(label= round(mean_prize_age,2)),nudge_y = 2)
   
```

## Q4: Which are the ten birth countries with the most Nobel Prize winners?
```{r }
filter(Laureate, bornCountry!="" ) %>%  group_by(bornCountry) %>% tally() %>% arrange(n)%>% 
  mutate(bornCountry=factor(bornCountry, levels=bornCountry)) %>% tail(10)%>%
  ggplot(aes(x= bornCountry, y = n,fill = bornCountry))+geom_bar(stat = "identity")+
  labs(title ="The ten birth countries with the most Nobel Prize winners" , x= "Country", y = "The number of Nobel Prize winner")+
  theme(axis.text.x = element_text(angle = 50, hjust = 1))+geom_text(aes(label= n),nudge_y = 10)
```

## Q5: Which are the ten death countries with the most Nobel Prize winners?
```{r }
filter(Laureate, diedCountry!="" ) %>%  group_by(diedCountry) %>% tally() %>% arrange(n)%>% 
  mutate(diedCountry=factor(diedCountry, levels=diedCountry)) %>% tail(10)%>%
  ggplot(aes(x= diedCountry, y = n,fill = diedCountry))+geom_bar(stat = "identity")+
  labs(title ="The ten death countries with the most Nobel Prize winners" , x= "Country", y = "The number of Nobel Prize winner")+
  theme(axis.text.x = element_text(angle = 50, hjust = 1))+geom_text(aes(label= n),nudge_y = 10) 
```

## Q6: What is ratio of male and female winners in each category?
```{r }
Laureate %>% filter(gender == "male" | gender == "female") %>% 
  group_by(category,gender)%>% tally() %>%  mutate(prop = round((n/ sum(n)),3))  %>% 
  ggplot(aes( x= "" , y = prop, fill = gender)) +
  geom_bar(width = 1, stat = "identity")+ geom_text(aes(label= percent(prop)),size=5,position = position_stack(vjust = 0.5))+ 
  labs(title = "The ratio of male and female winners in each category", x="", y = "")+
    facet_wrap(~category)+coord_polar("y",start = 0)+
  theme_minimal()+theme(axis.ticks = element_blank(), 
                        axis.text.y = element_blank(),
                        axis.text.x = element_blank()) 
```

## Q7: What is the migration pattern between the birth country and death country of Nobel laureates?
```{r }
filter(Laureate, bornCountry!="" ) %>%  group_by(bornCountry) %>% tally() %>% arrange(n)%>%
  tail(10) 
Laureate %>% filter(bornCountry!="" & diedCountry != ""& bornCountry != diedCountry)%>%
  mutate(Top10_BirthCountry = case_when(
    bornCountry == "USA" ~ "USA",
    bornCountry == "Germany" ~ "Germany",
    bornCountry == "United kingdom" ~ "United kingdom",
    bornCountry == "France" ~ "France",
    bornCountry == "Sweden" ~ "Sweden",
    bornCountry == "Poland" ~ "Poland",
    bornCountry == "Japan" ~ "Japan",
    bornCountry == "Italy" ~ "Italy",
    bornCountry == "the Netherlands" ~ "the Netherlands",
    bornCountry == "Russia" ~ "Russia",
    TRUE ~ "Others" 
    ))%>% ggplot(
  aes(x=0, y = bornCountry, xend= diedCountry, yend = 0, color = Top10_BirthCountry))+
  geom_curve(curvature = -0.5)+ scale_x_discrete() + scale_y_discrete() +
 theme_minimal()+
  theme( panel.grid = element_blank(),
    plot.background = element_rect(fill = "grey"),
    axis.text.x = element_text(angle = 50, hjust = 1),plot.title = element_text(hjust = 0.45))+ labs( x = "Death Country", y ="Birth Country")+ ggtitle("The migration pattern between the birth country and death country of Nobel laureates")
```

## Q8: What are the trends in the age of Nobel Prize winners in each category?
```{r }
Laureate %>% filter(substr(born,1,4) != "0000") %>% 
  mutate(prize_age = as.numeric(year) - as.numeric(substr(born,1,4))) %>% group_by(category)%>% 
  ggplot(aes(x= year, y = prize_age)) + geom_smooth(method ="lm")+ geom_point()+
  labs(x= "year", y ="the age of the prize winners",title = "Average age of Nobel Prize winners by category")+facet_wrap(~category)+scale_x_continuous(breaks = seq(1900, 2016, 20))
```